### 2025-04-18 mixed-models.qmd
20250418 - diagnostic plots

```{r}
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("bbmle")
library("rstan")
library("brms")
library("cmdstanr") # todo: install.packages("cmdstanr", repos = c("https://stan-dev.r-universe.dev", getOption("repos"))); check_cmdstan_toolchain(); cmdstanr::install_cmdstan()
library("fitdistrplus")
library("parallel")
library("parallelly")
library("plotly")
library("viridis")
library("tidyverse")
```

@@

>>>>

```{r}
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("bbmle")
library("rstan")
library("brms")
library("cmdstanr") # todo: install.packages("cmdstanr", repos = c("https://stan-dev.r-universe.dev", getOption("repos"))); check_cmdstan_toolchain(); cmdstanr::install_cmdstan()
library("fitdistrplus")
library("performance")
library("parallel")
library("parallelly")
library("plotly")
library("viridis")
library("tidyverse")
```

@@

#### Diagnostic Plots {#sec-fantasyPointsByAgeExperienceModelsDiagnosticPlots}

##### Plot of Residuals {#sec-fantasyPointsByAgeExperienceModelsResidualPlot}

```{r}
plot(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)

plot(
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  type = c("p","smooth"),
  col.line = 1)
```

##### Scale-Location Plot {#sec-fantasyPointsByAgeExperienceModelsScaleLocationPlot}

```{r}
plot(
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  sqrt(abs(resid(.))) ~ fitted(.),
  type = c("p","smooth"),
  col.line = 1)
```

##### Quantile–Quantile (QQ) Plot {#sec-fantasyPointsByAgeExperienceModelsQQPlot}

```{r}
qqnorm(resid(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience))
qqline(resid(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience))
```

##### Probability–Probability (PP) Plots {#sec-fantasyPointsByAgeExperienceModelsDiagnosticPPPlots}

```{r}
petersenlab::ppPlot(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
```

##### Residuals Versus Leverage Plot {#sec-fantasyPointsByAgeExperienceModelsResidualsVsLeveragePlot}

```{r}
plot(
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  rstudent(.) ~ hatvalues(.))
```

##### Other Diagnostic Plots {#sec-fantasyPointsByAgeExperienceModelsOtherDiagnosticPlots}

```{r}
performance::check_model(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
```
